Adversarial State Aggregation

### 2019-11-22 minutia/paper/paper.tex

    \section{Introduction}
    Although state aggregation may not generalize as well as methods based on neural networks, the techniques has
    both analytical and practical advantages. In camparison, state aggregation takes less computation power to
    compute representative features. Moreover, analysis and troubleshooting in a state aggregation process is more
    obvious than a black-box neural network. Approximation is a corner stone in all successfull RL methods to hold a
    "good" mapping between a large state space to a much smaller one where in value function is computable or at
    lesast feasible. These "good" approximators end up with "good" features to represent the projected state space.

    Reassuring achievements in the Deep RL in a variety of fields absorb the attention from the community
    \citep{Mnih2015, schulman2015a, Lillicrap2015, silver2016a}. The cross
    fertilization in using approximation techniques by Deep Neural Networks in solving immense state space problems
    in RL is a key. While the newly emerged methods are growing at a staggering pace, a parallel area of research
    has been formed wherein a variety of techniques have been utilized to make these methods contravene their
    promised functionality. These efforts would be served to develop robustness in those spectacular models and
    reduce their susceptibility to data tampering or dynamics of the environment. Robustness ---as a property in
    machine learning--- elevates assurance about methods performance and their reliability to the foreground. In a
    few studies \cite{Goodfellow2014}  vulnerabilities of DNN's to adversarially-manipulated inputs are revealed.
    Therefore, robust algorithms, have to be of paramount importance in applying deep RL to real world scenarios to
    mitigate risks of implementation. Adversarial attacks as a way to perturbing these algorithms, are introduced in
    recent works \cite{Huang2017, Kos2017} from different aspects to degrade algorithms' performance. One of such
    potentials are changes in the environment dynamics.

@@

    \section{Related Work}
    \cite{Goodfellow2014} stated and consequently depicted that the root cause of vulnerability to adversarial
    examples laid behind the piecewise linearity attributes of neural network models.

@@

    \subsection{Adversarial attacks}
    The designed attack may have different levels of access to the underlying training policy which have motivated
    the community to classify adversarial attacks into two distinct categories, namely \textit{white-box} or
    \textit{black-box} attacks. White-box attacks illustrating the scenario in which the... Adversarial attacks fall
    in either one of the following categories based upon the stage which in the adversary perturbs the model:
    \begin{itemize}
        \item Train time: Data poisoning.
        \item Evaluation time: Adversarial examples.
        \item Deploy time: Black-box attacks.
    \end{itemize}

>>>>

    \section{Introduction}
    Real-world problems embody high-dimensional state spaces where in computational issues
    arise.
    Various approximation methods are proposed in the literature to reduce the resulted value function
    dimensionality \cite{Sutton1998, Francois-Lavet2018}.
    State aggregation is one of the simplest and most analytically transparent state representation approximation.

    Although state aggregation may not generalize as well as neural network-based methods, the techniques has both
    analytical and practical advantages \cite{Lagoudakis2003}.
    In comparison, state aggregation takes less computation power to calculate representative features.
    Moreover, analysis and troubleshooting in a state aggregation process is more obvious than a black-box neural
    network.
    Approximation is a corner stone in all successful RL methods to hold a "good" mapping between a large state
    space to a much smaller one where in value function is computable or at least feasible.
    These "good" approximators can end up with "good" features to represent the projected state space.

    The cross-fertilization in using state aggregation and deep neural networks in solving immense state
    space problems in RL is also profound.
    While the newly emerged methods are growing at a staggering pace, a parallel area of research has been formed
    wherein a variety of techniques have been utilized to make these methods contravene their promised functionality.
    These efforts would be served to develop robustness in those spectacular models and reduce their
    susceptibility to data tampering or dynamics of the environment.

@@

@@

    \subsection{Adversarial attacks}
    The designed attack may have different levels of access to the underlying training policy which have motivated
    the community to classify adversarial attacks into two distinct categories, namely \textit{white-box} or
    \textit{black-box} attacks. White-box attacks illustrating the scenario in which the... Adversarial attacks fall
    in either one of the following categories based upon the stage, which in the adversary perturbs the model:
    \begin{itemize}
        \item Train time: Data poisoning.
        \item Evaluation time: Adversarial examples.
        \item Deploy time: Black-box attacks.
    \end{itemize}
